%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{textcomp}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=black,
}
 
\urlstyle{same}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{KARTIK SRIVASTAVA} % Your name
\address{C-322, The Greens, Doddanekkundi, Bengaluru, Karnataka. PIN: 560037} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+91) 77 299 07666 \\ kartiksrivastava144@gmail.com}  % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

%\begin{rSection}{OBJECTIVE}

%{Recently graduated, multidisciplinary Engineer with excellent problem solving abilities and process-thinking skill seeks hands on experience within a company that embraces creativity and innovation.Through my studies, I have gained extensive knowledge of production and manufacturing engineering, product design, among many other components of  Mechanical Engineering.Effective communicator who builds positive, cohesive relationship with all level of staff, eager to put my extensive studies to practical, applied use.}


%\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Birla Institute of Technology and Science, Pilani - Hyderabad Campus}  \hfill{2014 - 2019}
\\ Bachelor of Engineering (Hons.) in Computer Science \hfill {}
\\ Master of Science (Hons.) in Mathematics
\\{\bf CGPA: 8.08/10.00}  
\\(\textit{First Division})

{\bf City Montessori School - Gomti Nagar, Lucknow} \hfill {2014}
\\ Indian School Certificate (ISC) Examination
\\ {\bf Percentage: 93.67\%}

{\textbf{St. Francis' College, Lucknow}}  \hfill {2012}
\\Indian Certificate of Secondary Education (ICSE)
\\{\bf Percentage 90.14\%}


%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{SKILLS and
%INTERESTS}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Skills & Production and Manufacturing Engineering, Automobile Engineering, CAD/CAM,\\ 
%Interests & Mechanical Part Design,Optimization,Quality Control and Assurance,Product Development\\  
%Design Software & Autocad, Creo, SolidWorks \\
%Platforms &  MS Word,C  \\
%\end{tabular}

%------------------------------------------------------------
%------------------------PUBLICATIONS------------------------
%------------------------------------------------------------

%\end{rSection}
\begin{rSection}{PUBLICATIONS}

\begin{rSubsection}{Multi Modal Semantic Segmentation using Synthetic Data}{2019}
{\textbf{Kartik Srivastava}, Akash Kumar Singh, Guruprasad M. Hegde}{}
\\{Accepted in workshop on \textit{Deep learning for Automated Driving: Beyond Perception (DLAD-BP 2019)}, IEEE International Conference on Intelligent Transportation Systems 2019 (ITSC \textquotesingle19). \textbf{[}\href{https://arxiv.org/abs/1910.13676}{\textbf{pdf}}, \href{https://sites.google.com/view/dlad-bp-itsc2019/schedule?authuser=0\#h.p_gI84BCoB0_bJ}{\textbf{link}}\textbf{]}} 
 
\end{rSubsection} 
\end{rSection} 

%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{INDUSTRY EXPERIENCE}

\begin{rSubsection}{Amazon Web Services, Bangalore}{}
{\textbf{Software Development Engineer}}{December 2019 - Present}
\\ Currently working in the Control Plane team of AWS Elasticsearch service, where my work is focused on providing Elasticsearch as a fully managed and scalable service.
 
\end{rSubsection} 

\begin{rSubsection}{Amazon Development Center, Bangalore}{}
{\textbf{Software Development Engineer}}{July 2019 - December 2019}
\\ Worked with the Worldwide Deals team of Amazon and was responsible for maintaining various tier-2 services that facilitate creation and management of deals on Amazon retail website.
 
{\textbf{\textit{Software Development Engineering Intern}}}{\hfill \textit{May 2018 - July 2018}}
\\{\textit {Data Warehouse Migration}}
\\ Worked with the Deals \& Events team of Amazon and migrated their noSQL databases to SQL based Oracle Data Warehouse to enable backwards compatibility of data for business and analytics teams of Amazon. The project involved conversion of unstructured data from noSQL databases to structured data (tab separated values) using functional programming and loading it into relational data warehouses through ETL jobs. 
 
\end{rSubsection} 


%------------------------------------------------

\begin{rSubsection}{Essar Power Gujarat Ltd.(EPGL) - Jamnagar, Gujarat}{May 2016 - July 2016}{\textbf{Summer Intern}}{}
\\{\textit{Analysis of the Conveyor Belt System of Coal Handling Plant-EPGL}}
\\ Analyzed the breakdown and working pattern of the conveyor belt system of Coal Handling Plant(CHP) of EPGL.
Calculated the current reliability and approximated the reliability function of the system. 
\end{rSubsection}
\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\pagebreak

\begin{rSection}{RESEARCH EXPERIENCE}

\begin{rSubsection}{Robert Bosch Engineering and Business Solutions, Bangalore}{January 2019 - July 2019}
{Research Intern - Computer Vision Group, Research \& Technology Center}{}
\\{\bf Multi Modal Semantic Segmentation using Synthetic Data}\\
Worked on developing methods for generating artificial data using CARLA for semantic segmentation of LIDAR point clouds used in autonomous driving vehicles. The work majorly focused on the feasibility of using artificial data from driving simulators for training machine learning models for 3D semantic segmentation. 
\end{rSubsection}

\begin{rSubsection}{Nanyang Technological University, Singapore}{August 2018 - December 2018}{Research Intern (Supervisor: Assoc. Prof. Chng Eng Siong)}{}
\\{\bf Text Imputation using Recurrent Neural Networks}
\\ Developed a computational model for text imputation using recurrent neural networks. The proposed model uses a bidirectional LSTM and attention mechanism to predict the missing word in the sentence. 
%The project involves building an  efficient language model that scores rare words (such as Singaporean named entities from a small corpus) at par with its more common counterparts (named entities from a larger corpus) as candidates for the missing word.
 
\end{rSubsection} 


%------------------------------------------------

\begin{rSubsection}{MEnutritious, New Delhi}{May 2017 - July 2017}{Research Intern}{}
\\{\bf Recipe Parser for feature extraction}
\\ Developed a rule-based recipe parser using python and NLTK that detects and extracts various features from food recipes. The parser interprets natural language and extracts various entities like ingredients, quantity, unit, tools used, and various other attributes of the recipe like temperature and actions.
\end{rSubsection}
\end{rSection} 

%----------------------------------------------------------------------------------------

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{RESEARCH PROJECTS} \itemsep -3pt  

% {\bf Study of the basics of Natural Language Processing} \hfill {\it January 2018 - May 2018}\\ 
% {\it Supervisor: Assoc. Prof. Aruna Malapati (BITS Pilani, Hyderabad Campus)}
% \\ The project involved the study of basics of natural language processing with focus on applications of machine learning to NLP. 

% {\bf Study oriented Project on Applications of Machine Learning to Natural Language Processing}\\  
% {\it Supervisor: Assoc. Prof. Aruna Malapati (BITS Pilani, Hyderabad Campus)}{ \hfill {\it January 2018 - May 2018}}
% \\ The project involved literature review of applications of machine learning to natural language processing. It also included the study of various neural network architectures used in NLP tasks and their hands-on implementation. 

{\bf Automatic Summarization of Tweets } \hfill {\it August 2017 - November 2017}\\ 
{\it Supervisor: Mr. Surender Singh Samant (BITS Pilani, Hyderabad Campus)}
\\The project involved generating summaries of tweets using graph-based statistical summarization technique - Phrase Reinforcement Algorithm. The system generated summaries were compared with the human generated summaries using the ROUGE-1 evaluation metric. These results were used to tune the hyper-parameters of the algorithm. 

{\bf Information Retrieval System for Music Lyrics} \hfill {\it August 2017 - November 2017}\\ 
{\it Supervisor: Assoc. Prof. Aruna Malapati (BITS Pilani, Hyderabad Campus)}
\\ Constructed a vector-space information retrieval system that retrieved the details of the song on consuming the lyrics of the song as input. Also created a python based GUI for the project.

{\bf Point distribution generation for meshless solvers } \hfill {\it January 2017 - May 2017}\\ 
{\it Supervisor: Dr. N. Anil (BITS Pilani, Hyderabad Campus)}
\\ The project involved generating dense point distributions for two-dimensional geometries using quadtrees by taking the boundary points of the geometry as input. The generated distribution serves as an input to a numerical solver which can calculate flow of a fluid over the body of the geometry. 

{\bf Face Recognition Using Artificial Neural Networks} \hfill {\it January 2017 - May 2017}\\ 
{\it Supervisor: Assoc. Prof. N.L. Bhanumurthy (BITS Pilani, Hyderabad Campus)}
\\ Developed a shallow artificial neural network to recognize face, pose and presence of sunglasses. The neural network was able to correctly recognize from 20 faces and 4 different poses(left, right, center and down) and gave a peak accuracy of 92\%-100\%.  

\end{rSection} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% SKILLS AND TECH PROFICIENCY%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{TECHNICAL PROFICIENCY}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages(Proficient) & C, Python, Java, Scheme \& Bash\\ 
Languages(Familiar) & C++, Assembly(x86), MIPS, MySQL, Prolog, MATLAB \& LaTeX \\  
Programming Frameworks: & PyTorch \& Tensorflow  \\
\end{tabular}

\end{rSection}

\pagebreak
\begin{rSection}{Relevant Coursework}
{\bf Computer Science}\\
Data Structures and Algorithms, Design and Analysis of Algorithms, Machine Leaning, Information retrieval, Database Systems, Object Oriented Programming, Discrete Mathematics, Logic in Computer Science, Operating Systems, Computer Networks, Computer Architecture, Theory of Computation, Principles of Programming Languages, Compiler Construction, Microprocessors and Interfacing \& Digital Design.
\\ \\
{\bf Mathematics}\\
Mathematics (Multi-variable Calculus, Linear Algebra, Probability and Statistics),Linear Optimization, Non-linear Optimization, Graphs and Networks, Operations Research, Numerical Analysis, Fuzzy Logic and Applications, Number Theory and Game Theory.
\end{rSection}

\begin{rSection}{TEACHING EXPERIENCE}
{\bf Teaching assistant for Database Systems}{\hfill \it January 2018 - May 2018}
\\ Responsibilities included assisting with lab sessions and invigilating lab examinations and quizzes. \\ \\
{\bf Teaching assistant for Mathematics I (Multi - Variable Calculus)}{\hfill \it August 2017 - December 2017}
\\ Responsibilities included invigilating quizzes and helping the instructors with grading papers.

\end{rSection}

\begin{rSection}{AWARDS AND RECOGNITION}
{\bf Merit-cum-need scholarship}
{\hfill \it Birla Institute of Technology and Science, Pilani}
\\ Recipient of merit-cum-need scholarship for all semesters of education at Birla Institute of Technology and Science, Pilani - Hyderabad Campus. The scholarship is awarded to the top 24\% students and covers upto 80\% of tuition fee. \\ \\
{\bf Research Travel Grant}
{\hfill \it Birla Institute of Technology and Science, Pilani}
\\ Recipient of travel grant for pursuing thesis in Computer Science at Nanyang Technological University, Singapore.

\end{rSection}

\begin{rSection}{VOLUNTEERING}
{\bf Make a Difference (MAD)}\\
{\bf \textit{Academic Support Volunteer}} {\hfill \it July 2019 - January 2020}\\
Actively volunteering to teach underprivileged high school students in shelter homes and helping MAD to achieve it\textquotesingle s goal to ensure that all children in need of care and protection are able to realize long-term outcomes equitable with the middle-class.

\end{rSection}

%----------------------------------------------------------------------------------------
%\begin{rSection}{Co-curricular Activities} 
% \itemsep -1pt {}   
% \item STTP on "Life Long Research" in SVNIT,Surat \hfill February 2016
% \item Design War Cad, SRCOE, Rajkot, Secured 2rd rank in a state level competition\hfill January-2016
% \item  Design War Cad, B.H Gardi, Rajkot, Secured 2rd rank in a
% state level competition. \hfill January-2014 
% \item Participated in National Level Technical Symposium Festival Edge and Above, SVIT, Vasad. \hfill February-2013
% \item Participated in National Level Technical Symposium Festival Home Basix, SVIT, Vasad.
%  \hfill  February-2013 
% \item Participated in National Level Technical Symposium Rise of Machine, SVIT, Vasad,  \hfill March-2014 \itemsep -1pt {}   
% \item STTP on "Life Long Research" in SVNIT,Surat \hfill February 2016
% \item Design War Cad, SRCOE, Rajkot, Secured 2rd rank in a state level competition\hfill January-2016
% \item  Design War Cad, B.H Gardi, Rajkot, Secured 2rd rank in a
% state level competition. \hfill January-2014 
% \item Participated in National Level Technical Symposium Festival Edge and Above, SVIT, Vasad. \hfill February-2013
% \item Participated in National Level Technical Symposium Festival Home Basix, SVIT, Vasad.
%  \hfill  February-2013 
% \item Participated in National Level Technical Symposium Rise of Machine, SVIT, Vasad,  \hfill March-2014 
 
% {\bf Core member}{ \hfill \it 2015-2016}\\
% {\it AXIOM, Mathematics Association,BITS Pilani, Hyderabad Campus} \\Organizer of many mathematics competitions during technical fest ATMOS 2015.


% {\bf Member}{\hfill \it 2014-16}\\
% {\it Department of Security and Hospitality, BITS Pilani, Hyderabad Campus}
% \\Handled security and Logistics Operations of various events during all the fests.
% \end{rSection}

\end{document}
